Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-04 paper/preprint/appendix.Rmd
add commented code for prf on center detections

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))

@@

```{r}
# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) 
```

@@

@@

>>>>

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData'))

@@

```{r}
# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))

    # mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center)) 
```

@@

# function to return prfs
 return_prf_short = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
 }

@@

```{r}
# Evaluating prfs in center detections is challenging because we ONLY have ground truth on the full image -- so it's not that informative.

# return_prf_short(gold_sample$hand_eval_ketan_center)
# return_prf_short(gold_sample$face_eval_ketan_center)
```
